Joint Likelihood Deconvolution of Astronomical Images in the Presence of Poisson Noise

### 2023-09-26 src/tex/ms.tex
[showyourwork] overleaf sync

    \begin{figure*}
        \script{chandra-e0102-zoom-a.py}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/chandra-e0102-zoom-a.pdf}
            \caption{
                The left panel shows the flux and counts profile of the region illustrated in the right panel. The associated $2\sigma$ error band estimated using the bootstrap method is shown transparent in the background.
            }
            \label{fig:chandra-e0102-zoom-a}
        \end{centering}
    \end{figure*}

>>>>

    \begin{figure*}
        \script{chandra-e0102-zoom-a.py}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/chandra-e0102-zoom-a.pdf}
            \caption{
                The left panel shows the deconvolved flux and counts profile of the region illustrated in the right panel. The associated $3\sigma$ error band is shown transparent in the background. Both profiles are normalized such that they integrate to unity and are aligned such that the position of their peak coincides.
            }
            \label{fig:chandra-e0102-zoom-a}
        \end{centering}
    \end{figure*}
